---
title: "Data Science Project"
author: "Liza Pikovsky, Matanel Zoldan, Osnat Versulker, Shaul Ora, Netanel Malka"
date: "24 6 2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(CATT)
library(dbplyr)
library(dplyr)
library(ggplot2)
library(Hmisc)
library(htmlTable)
library(htmltools)
library(HTMLUtils)
library(htmlwidgets)
library(knitr)
library(markdown)

library(rmarkdown)
library(tidyverse)
library(scatterplot3d)
library(rgl)
library(plotrix)
lana.pro <- read.csv("codnew4.csv") 

```


##  
The education system in Israel is divided into several types that combine online learning tools. When,
On the one hand, schools that encourage activity in computerized systems to enter grades and monitor students. And on the other hand, low-awareness schools use these systems, preferring manual monitoring by teachers. As part of our undergraduate studies in industrial engineering and management, we conduct research.
The aim of the study is to understand the difficulties that teaching staff face and how much change and accessibility is needed in the computerized systems in the education systems. 


##  Statistic analysis
Median year of birth of the person who answered the survey 
```{r}
median(lana.pro$date.b) 
```
Average weekly hours
```{r}
mean(lana.pro$sum.hour)
```
Standard deviation of learning from shopping
```{r}
sd(lana.pro$techno.1) 

```





## The Cochran-Armitage Trend Test
The Kokran-Armitage test is a variation of a live-squared test that is suitable for assessing the trend of the relationship between two qualitative variables, one of which is measured on a arranged scale of measurement, and the other receives only two values. Unlike a quadratic live test, this test takes into account the fact that there is an order between the values of the ordered variable. This test is a particular case of the M square test.



```{r}
CATT(lana.pro$sex,lana.pro$techno)
```
According to the value of p-value, it can be seen that the female sex has high technological abilities.


## Graphs

1. Distribution of answers by region
2. Age distribution of the respondents
3. Seniority in the face of technological capabilities
4. Distribution by sector
5. Distribution of hours by number of classes
6. The effect of seniority on frontal school hours
7. Division by species
8. Does long-term online learning have an impact
9. Use of online courses - universities versus colleges
10. Number of online study hours during the corona period

## 1. Distribution of answers by region

```{r}
pie.aera <- table(lana.pro$area)
names(pie.aera) <- c("Jerusalem" , "North" ,  "Haifa" ,  "Center" ,  "Tel-Aviv" , "South" , "Jehuda & Samaria")
pie3D(pie.aera,labels=names(pie.aera),explode=0.1,
   main="Pie Chart of Counties")


```

##  2. Age distribution of the respondents

```{r}
hist(lana.pro$date.b ,main ="Age distribution" ,xlab = "year", ylab = "people")

```

## 3. Seniority in the face of technological capabilities

```{r}
ggplot(data=lana.pro,mapping=aes(x=veteq ,y=techno))+
  geom_jitter(position=position_jitter(0.2))+
  labs(title="Seniority vs technological capabilities",
       x="Seniority",
       y = "technological capabilities")

```


## 4. Distribution by sector
explanation:
0 = state
1 = State religious
2 = Haredi


```{r}
ggplot(data = lana.pro,aes(migzar))+
  geom_bar()+
  labs(title="Educational institution sector",
       x="Sector",col="darkblue")
```

## 5. Distribution of hours by number of classes
It can be seen that as the number of classes a teacher teaches in them increases the distribution of hours he will teach decreases 
```{r}
ggplot(data = lana.pro, aes(sum.hour,num.lev))+  
  geom_violin(fill="blue")+
  labs(title="Number of hours distributed over the number of classes",x="Amount of frontal hours", y = "Num of classes")+
  theme_classic()
```


##  6. The effect of seniority on frontal school hours
```{r}
ggplot(lana.pro)+
  geom_col(fill = "lightblue",
           color = "black",
           aes(x = sum.hour ,y = veteq))+
  geom_label(aes(x = sum.hour,
                 y = veteq,
                 label = paste0(round(veteq, 0), "%"))) +
  ggtitle("Effect of study seniority on the number of frontal hours",
          subtitle = "Based on 2020 survey")
```

## 7. Distribution by gender
 
1 = Female
0 = Male

```{r}
ggplot(data = lana.pro, aes(sex ,color="steelblue"))+
  geom_bar()+
  labs(title="Distribution by gender",
       x="Gender")

```

## 8. Does long-term online learning have an impact
It can be seen from the graph that distance learning has strengthened mastery of online teaching and in the future they want to continue. 
```{r}
ggplot(data = lana.pro,aes(COVID.19 , merahok))+
  geom_raster()+
  labs(title="Has online learning strengthened the control of online teaching?",
       x="Online learning",
       y = "Future application")

```


## 9. Using Online Courses

1 = Colleges
2 = Universities

```{r}


ggplot(data = lana.pro,aes(mosad,cuors))+
  geom_jitter(position=position_jitter(0.2))+
  labs(title="Using Online Courses - Universities vs. Colleges",
       x="Type of institution",
       y = "Online courses")

```


## 10. Study hours online during the Corona time
It can be seen that Ruth the teachers taught between 10 and 15 hours of study per week during this period.
```{r}
boxplot(lana.pro$techno.1, main = "Study hours online during the Corona",
        xlab = "Hours",
        ylab = "COVID 19",
        col = "orange",
        border = "brown",
        horizontal = TRUE,
        notch = TRUE)

```


## Relationship between routine study hours and the corona period
QQPLOT graph that analyzes the relationship between frontal study hours and online study hours
It can be seen that there is a gap between the normal hours and the corona hours.
```{r}

qqplot(x = lana.pro$sum.hour,
       y = lana.pro$techno.1,
       xlab = "Frontal hours in routine",
       ylab = "Online hours during the Corona",
       main = "The relationship between school hours in the routine and the Corona period")


```
## The conclusions
As we understand, significant improvement is needed in the field of online learning in schools. Corona has challenged the teams and proved that mastering online classes requires learning and improvement.
A large proportion of respondents agreed that if the school had sent them to an online course this would have helped in understanding the computerized system.

